Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-02 paper.tex
Copy over info from the 2local slides

Here we describe the scheme between the classical client and an honest quantum server.

@@

First, we rewrite the circuit to consist of only controlled phase gates and 1-qubit gates. TODO: prove that these 1-qubit gates are all real. We then double (TODO maybe multiply by $\gamma$ instead of doubling?) the size of the circuit by padding identity matrices at the end.

\subsection{2-local Hamiltonian construction}

We then attempt to construct a 2-local Hamiltonian with ground state $$\phi=\sum_{t=0}^TU_t...U_1|x\rangle\otimes|\hat{t}\rangle$$.

We then follow the rest of \cite{quant-ph/0406180} and reduce the circuit into a 2-Local Hamiltonian instance. We can then turn all the Hamiltonians involved into some combinations of $X$ and $Z$ matrices following \cite{0704.1287}.
It will drop the $H_{out}$ term and simply set $H=J_{in}H_{in}+J_2H_{prop2}+J_1H_{prop1}+J_{clock}H_{clock}$.

>>>>

Here we describe the scheme between the classical client and an honest quantum server.
Let $x$ be the client's input, and $U_T...U_1$ be the circuit to evaluate.

@@

First, we rewrite the circuit to consist of only controlled phase gates and 1-qubit gates. TODO: prove that these 1-qubit gates are all real. We ensure that each $C_\phi$s are preceded and followed by two $Z$ gates. That is, if the $C_\phi$ acts on the qubits $f_t$ and $s_t$, then the circuit would look like $Z_{f_t}Z_{s_t}C_\phi Z_{s_t}Z_{f_t}$ around each $C_\phi$. We then pad the circuit so that the $C_\phi$s are applied at $t\in T_2=\{L, 2L, 3L, \ldots\}$ for some $L\in\mathbb{N}$. Let $T_1=[T]\setminus T_2$ be time steps corresponding to 1-qubit gates.

We then double (TODO: maybe multiply by $\gamma>1$ instead of doubling?) the size of the circuit by padding identity matrices at the end.

\subsection{Constructing the 2-local Hamiltonian instance}

We then attempt to construct a 2-local Hamiltonian with ground state $$\phi=\sum_{t=0}^TU_t...U_1|x\rangle\otimes|\hat{t}\rangle$$. We do so by causing states perpendicular to this to have high eigenvalues.

First, we ensure that the invalid clock states have high eigenvalues. That is, we take $$H_{clock}=\sum_{1\leq i<j\leq T} I\otimes |01\rangle\langle01|_{ij}$$. We also set $S_{legal}=\ker H_{clock}$.
We note that when stricted to $S_{legal}$, 
\begin{itemize}
	\item $|10\rangle\langle10|_{t,t+1}
		=|\widehat{t}\rangle\langle\widehat{t}|$ 
	\item $|1\rangle\langle0|_{t+1}
		=|\widehat{t+1}\rangle\langle\widehat{t}|$
	\item $|11\rangle\langle00|_{t,t+1}
		=|\widehat{t+2}\rangle\langle\widehat{t}|$
\end{itemize}

Then, we ensure that 1-qubit gates are propagated properly. To do so, we set
	$$H_{prop1}=\sum_{t\in T_1}H_{prop,t}$$
	$$H_{prop,t}=I\otimes|\widehat{t}\rangle\langle\widehat{t}|
		+I\otimes|\widehat{t-1}\rangle\langle\widehat{t-1}|
		-U_t\otimes|\widehat{t}\rangle\langle\widehat{t-1}|
		-U_t^\dagger\otimes|\widehat{t-1}\rangle\langle\widehat{t}|$$

I probably need to explain why this works but I'll leave it for another day.

Let $S_{prop1}=\ker H_{prop1}$.
Then, $S_{prop1}$ has the following as basis:
\begin{itemize}
	\item $|00\rangle_{f_t,s_t}|\xi_{00}\rangle\otimes
		(|\widehat{t}\rangle+|\widehat{t+1}\rangle+|\widehat{t+2}\rangle)$
	\item $|01\rangle_{f_t,s_t}|\xi_{01}\rangle\otimes
		(|\widehat{t}\rangle+|\widehat{t+1}\rangle-|\widehat{t+2}\rangle)$
	\item $|10\rangle_{f_t,s_t}|\xi_{10}\rangle\otimes
		(|\widehat{t}\rangle-|\widehat{t+1}\rangle-|\widehat{t+2}\rangle)$
	\item $|11\rangle_{f_t,s_t}|\xi_{11}\rangle\otimes
		(|\widehat{t}\rangle-|\widehat{t+1}\rangle+|\widehat{t+2}\rangle)$
\end{itemize}

Also, if $t\in T_2$, that is, $t$ corresponds to a time step where $C_\phi$ is applied, then the following are true due to $C_\phi$ being surrounded by $Z$ gates:
\begin{itemize}
	\item $|0\rangle\langle0|_{f_t}\otimes
		|\widehat{t}\rangle\langle\widehat{t}|
		=(|\widehat{t}\rangle+|\widehat{t+1}\rangle)
		(\langle\widehat{t}|+\langle\widehat{t+1}|)$
	\item $|1\rangle\langle1|_{f_t}\otimes
		|\widehat{t}\rangle\langle\widehat{t}|
		=(|\widehat{t}\rangle-|\widehat{t+1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t+1}|)$
	\item $|0\rangle\langle0|_{s_t}\otimes
		|\widehat{t}\rangle\langle\widehat{t}|
		=(|\widehat{t+1}\rangle+|\widehat{t+2}\rangle)
		(\langle\widehat{t+1}|+\langle\widehat{t+2}|)$
	\item $|1\rangle\langle1|_{s_t}\otimes
		|\widehat{t}\rangle\langle\widehat{t}|
		=(|\widehat{t+1}\rangle-|\widehat{t+2}\rangle)
		(\langle\widehat{t+1}|-\langle\widehat{t+2}|)$
	\item $(|00\rangle\langle00|_{f_t,s_t}
		+|11\rangle\langle11|_{f_t,s_t})\otimes
		|\widehat{t}\rangle\langle\widehat{t}|
		=(|\widehat{t}\rangle+|\widehat{t+2}\rangle)
		(\langle\widehat{t}|+\langle\widehat{t+2}|)$
	\item $(|01\rangle\langle01|_{f_t,s_t}
		+|10\rangle\langle10|_{f_t,s_t})\otimes
		|\widehat{t}\rangle\langle\widehat{t}|
		=(|\widehat{t}\rangle-|\widehat{t+2}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t+2}|)$
\end{itemize}

Similarly,
\begin{itemize}
	\item $|0\rangle\langle0|_{f_t}\otimes
		|\widehat{t-1}\rangle\langle\widehat{t-1}|
		=(|\widehat{t-1}\rangle+|\widehat{t-2}\rangle)
		(\langle\widehat{t-1}|+\langle\widehat{t-2}|)$
	\item $|1\rangle\langle1|_{f_t}\otimes
		|\widehat{t-1}\rangle\langle\widehat{t-1}|
		=(|\widehat{t-1}\rangle-|\widehat{t-2}\rangle)
		(\langle\widehat{t-1}|-\langle\widehat{t-2}|)$
	\item $|0\rangle\langle0|_{s_t}\otimes
		|\widehat{t-1}\rangle\langle\widehat{t-1}|
		=(|\widehat{t-2}\rangle+|\widehat{t-3}\rangle)
		(\langle\widehat{t-2}|+\langle\widehat{t-3}|)$
	\item $|1\rangle\langle1|_{s_t}\otimes
		|\widehat{t-1}\rangle\langle\widehat{t-1}|
		=(|\widehat{t-2}\rangle-|\widehat{t-3}\rangle)
		(\langle\widehat{t-2}|-\langle\widehat{t-3}|)$
	\item $(|00\rangle\langle00|_{f_t,s_t}
		+|11\rangle\langle11|_{f_t,s_t})\otimes
		|\widehat{t-1}\rangle\langle\widehat{t-1}|
		=(|\widehat{t-1}\rangle+|\widehat{t-3}\rangle)
		(\langle\widehat{t-1}|+\langle\widehat{t-3}|)$
	\item $(|01\rangle\langle01|_{f_t,s_t}
		+|10\rangle\langle10|_{f_t,s_t})\otimes
		|\widehat{t-1}\rangle\langle\widehat{t-1}|
		=(|\widehat{t-1}\rangle-|\widehat{t-3}\rangle)
		(\langle\widehat{t-1}|-\langle\widehat{t-3}|)$
\end{itemize}

Now we ensure the 1-qubit gates are applied properly. The naive way would be to set
	$$H_t=I\otimes|\widehat t\rangle\langle\widehat t|
		+I\otimes|\widehat{t-1}\rangle\langle\widehat{t-1}|
		-C_\phi\otimes|\widehat t\rangle\langle\widehat{t-1}|
		-C_\phi^\dagger\otimes|\widehat{t-1}\rangle\langle\widehat{t}|$$
	$$H'=\sum_{t\in T_2}H_t$$
	Equivalently, $H_t=$

	$|00\rangle\langle00|_{f_t,s_t}\otimes
		(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$

	$|01\rangle\langle01|_{f_t,s_t}\otimes
		(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$

	$|10\rangle\langle10|_{f_t,s_t}\otimes
		(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$

	$|11\rangle\langle11|_{f_t,s_t}\otimes
		(|\widehat{t}\rangle+|\widehat{t-1}\rangle)
		(\langle\widehat{t}|+\langle\widehat{t-1}|)$

However, this cannot be turned into 2-local, so we change the coefficients and set 
	$$H_{prop2}=\sum_{t\in T_2}H_{prop2,t}$$

	$H_{prop2,t}=$

	$|00\rangle\langle00|_{f_t,s_t}\otimes
		4(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$

	$|01\rangle\langle01|_{f_t,s_t}\otimes
		2(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$

	$|10\rangle\langle10|_{f_t,s_t}\otimes
		2(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$

	$|11\rangle\langle11|_{f_t,s_t}\otimes
		(|\widehat{t}\rangle+|\widehat{t-1}\rangle)
		(\langle\widehat{t}|+\langle\widehat{t-1}|)$
instead.

Now, if restricted to $S_{prop}$,

	$H_{prop2,t}=H_{qubit,t}+H_{time,t}=$
	$$(-2|0\rangle\langle0|_{f_t}-2|0\rangle\langle0|_{s_t}
		+|1\rangle\langle1|_{f_t}+|1\rangle\langle1|_{s_t})\otimes$$
	$$(|\widehat{t}\rangle\langle\widehat{t-1}|+
		|\widehat{t-1}\rangle\langle\widehat{t}|)+$$
	$$(2|0\rangle\langle0|_{f_t}+2|0\rangle\langle0|_{s_t}
		+|1\rangle\langle1|_{f_t}+|1\rangle\langle1|_{s_t}
		-2|01\rangle\langle01|_{f_t,s_t}
		-2|10\rangle\langle10|_{f_t,s_t})\otimes$$
	$$(|\widehat{t-1}\rangle\langle\widehat{t-1}|+
		|\widehat{t}\rangle\langle\widehat{t}|)$$

Lastly, we check if the input is right...
	$$H_{in}=\sum_{i=m+1}^N|1\rangle\langle1|_i\otimes|0\rangle\langle0|$$

Now we use the projection lemma here. This step is different now that $H_{out}$ is gone. I think $J_{in}$ gets dropped or something like that?
